### 2021-07-08 doc/thesis/chapters/dsp.tex
more diagrams

\includepicture [0.9] [0] {
  Signal spectrum, explaining the process of down-conversion.\\
  Diagram A) $f_s$ is high enough and thus meets the theorem.\\
  Diagram B) $f_s$ exactly meets the theorem.\\
  Diagram C) $f_s$ is too low and thus creates overlaps of the spectral replicas - aliasing \cite{ThyagarajanK.S2019ItDS}.
} {aliasing_freq_spectrum} {img/draw.io/sampling-aliasing}

>>>>

\includepicture [0.9] [0] {
  Frequency spectrum of the sampled baseband signal with its replicas at integer multiples of $f_s$ \cite{ThyagarajanK.S2019ItDS}.\\
  A) $f_s > 2f_{signal}$: $f_s$ is high enough and thus meets the theorem.\\
  B) $f_s = 2f_{signal}$: $f_s$ exactly meets the theorem.\\
  C) $f_s < 2f_{signal}$: $f_s$ is too low and thus creates overlaps of the replicas - aliasing.
} {aliasing_freq_spectrum} {img/draw.io/sampling-aliasing}
